---
title: "Aquamaps quality control"
output:
  html_document: 
    df_print: paged
    keep_md: no
    toc: no
    toc_float: yes
---

```{r setup, include="FALSE"}
#'========================================================================
# Aquamaps quality control
#'========================================================================
#
# by Mark R Payne
# DTU-Aqua, Kgs. Lyngby, Denmark
# http://www.staff.dtu.dk/mpay
#
# Created Wed Aug 21 14:07:22 2019
#
# <Description>
#
# This work is subject to a Creative Commons "Attribution" "ShareALike" License.
# You are largely free to do what you like with it, so long as you "attribute"
# me for my contribution. See the fine print at the end for exact details.
#
# To do:
#
# Notes:
#   * Knitting of notebooks from Rstudio leads to all sorts of messy problems 
#     with the directory. Use here::here() to specify a location relative to
#     the project top directory
#
#'========================================================================

#Configure Knitr
knitr::opts_chunk$set(
  echo=FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	results = "markup",
	fig.width = 10,
	fig.height=14/25*10,
  fig.align="center",
  fig.path=here::here("notebooks","figures","Missing_aquamaps_"))

#Powerpoint needs 14 x 25cm figures

# knitr::opts_knit$set(
#    root.dir="..")

library(tidyverse)
library(ggplot2)
library(tibble)
library(here)

theme_set(theme_bw(base_size = 14))
```

by Mark R Payne  <br>
DTU-Aqua, Kgs. Lyngby, Denmark  <br>
http://www.staff.dtu.dk/mpay  <br>
`r format(Sys.time(), "%a %b %d %Y, %H:%M:%S ")`

This notebook provides quality control of the Aquamaps database


## Missing species groups

```{r}
# Setup ---------------------------------------------------------------------------
species.db <- readRDS(here("objects/species_database.rds"))
amaps.meta <- readRDS(here("objects/Aquamaps/Aquamaps_meta.rds"))

#Make species.db tidy
species.db <-
  gather(species.db,"area","exemplar.species",starts_with("exemplar"))

knitr::kable(
  d<-filter(species.db,!(exemplar.species %in% amaps.meta$scientific.name)) ,
  booktabs = TRUE,
  caption = 'Groups missing from Aquamaps database.'
)
write_csv2(d,here("outputs/missing_aquamaps.csv"))

```

## Duplicated Aquamaps

A list of species where there is more than one aquamap for a given species

```{r}
dups <- amaps.meta$scientific.name[duplicated(amaps.meta$scientific.name)]
dups.all <- filter(amaps.meta,scientific.name %in% dups)
knitr::kable(dups.all,booktabs=TRUE)


```

Use this command to delete all speceis with duplicates

```{r eval=FALSE,echo=TRUE}
unlink(here("data/Aquamaps/maps",dups.all$fname))

```




***
*This work by Mark R Payne is licensed under a  Creative Commons
Attribution-NonCommercial-ShareAlike 3.0 Unported License. 
For details, see http://creativecommons.org/licenses/by-nc-sa/3.0/deed.en_US
Basically, this means that you are free to "share" and "remix" for 
non-commerical purposes as you see fit, so long as you "attribute" me for my
contribution. Derivatives can be distributed under the same or 
similar license.*

*This work comes with ABSOLUTELY NO WARRANTY or support.*

***



