---
title: "Species trait database"
output: 
  html_document:
    df_print: paged
    keep_md: no
    toc: yes
    toc_float: yes

---

```{r setup, include="FALSE"}
#'========================================================================
# Species trait database
#'========================================================================
#
# by Mark R Payne
# DTU-Aqua, Kgs. Lyngby, Denmark
# http://www.staff.dtu.dk/mpay
#
# Created Tue Aug 20 08:48:45 2019
#
# <Description>
#
# This work is subject to a Creative Commons "Attribution" "ShareALike" License.
# You are largely free to do what you like with it, so long as you "attribute"
# me for my contribution. See the fine print at the end for exact details.
#
# To do:
#
# Notes:
#   * Knitting of notebooks from Rstudio leads to all sorts of messy problems 
#     with the directory. Use here::here() to specify a location relative to
#     the project top directory
#
#'========================================================================

#Configure Knitr
knitr::opts_chunk$set(
  echo=FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	results = "markup",
	fig.width = 10,
	fig.height=14/25*10,
  fig.align="center",
  fig.path=here::here("notebooks","figures","Species trait database_"))

#Powerpoint needs 14 x 25cm figures

# knitr::opts_knit$set(
#    root.dir="..")

library(tidyverse)
library(ggplot2)
library(tibble)
library(here)

theme_set(theme_bw(base_size = 14))

```

```{r}
#==========================================================================
# Configure ####
#==========================================================================

```

by Mark R Payne  <br>
DTU-Aqua, Kgs. Lyngby, Denmark  <br>
http://www.staff.dtu.dk/mpay  <br>
`r format(Sys.time(), "%a %b %d %Y, %H:%M:%S ")`

This notebook provides an overview of data coverage for the species traits database

```{r}
#'========================================================================
# Setup ####
#'========================================================================
#Import trait database
trait.db <- 
  readRDS(here("objects/Species_database.rds")) %>%
  mutate(taxonomic.res=str_count(TAXOCODE,"X"))  

#Summary function

sum.fn <- function(x,trait) {
  sel <- 
    filter(x,is.na(x[trait])) %>%
    arrange(-taxonomic.res) 
  
  g <- ggplot(sel,aes(x=taxonomic.res))+
  stat_count()+
  labs(title=sprintf("Missing %s traits by taxonomic resolution",trait))
  
  print(g)
  
  return(sel)
}

```


## Coverage per trait

### Horizontal Habitat
```{r}
ggplot(trait.db, aes(x=horizontal.habitat))+
  stat_count()

sum.fn(trait.db,"horizontal.habitat")

```





### Vertical Habitat


```{r}
ggplot(trait.db,aes(x=vertical.habitat))+
  stat_count()

sum.fn(trait.db,"vertical.habitat")

```

### Lifespan

Lifespan is a continous variable, so just need to look at the NAs
```{r}
sum.fn(trait.db,trait="Lifespan.n")

```

### Mobility

```{r}
ggplot(trait.db,aes(x=Mobility))+
  stat_count() 

sum.fn(trait.db,"Mobility")

```



***
*This work by Mark R Payne is licensed under a  Creative Commons
Attribution-NonCommercial-ShareAlike 3.0 Unported License. 
For details, see http://creativecommons.org/licenses/by-nc-sa/3.0/deed.en_US
Basically, this means that you are free to "share" and "remix" for 
non-commerical purposes as you see fit, so long as you "attribute" me for my
contribution. Derivatives can be distributed under the same or 
similar license.*

*This work comes with ABSOLUTELY NO WARRANTY or support.*

***



