---
title: "Species coverage by value"
output:
  html_document: 
    df_print: paged
    keep_md: no
    toc: yes
    toc_float: yes
---

```{r setup, include="FALSE"}
#'========================================================================
# Species coverage by value
#'========================================================================
#
# by Mark R Payne
# DTU-Aqua, Kgs. Lyngby, Denmark
# http://www.staff.dtu.dk/mpay
#
# Created Tue Aug 20 16:36:56 2019
#
#
# This work is subject to a Creative Commons "Attribution" "ShareALike" License.
# You are largely free to do what you like with it, so long as you "attribute"
# me for my contribution. See the fine print at the end for exact details.
#
# To do:
#
# Notes:
#   * Knitting of notebooks from Rstudio leads to all sorts of messy problems 
#     with the directory. Use here::here() to specify a location relative to
#     the project top directory
#
#'========================================================================

#Configure Knitr
knitr::opts_chunk$set(
  echo=FALSE,
	error = FALSE,
	message = FALSE,
	warning = FALSE,
	include = TRUE,
	results = "markup",
	fig.width = 10,
	fig.height=14/25*10,
  fig.align="center",
  fig.path=here::here("notebooks","figures","Species coverage by value_"))

#Powerpoint needs 14 x 25cm figures

# knitr::opts_knit$set(
#    root.dir="..")

library(tidyverse)
library(ggplot2)
library(tibble)
library(here)

theme_set(theme_bw(base_size = 14))
```

```{r}
#==========================================================================
# Configure ####
#==========================================================================

```

by Mark R Payne  <br>
DTU-Aqua, Kgs. Lyngby, Denmark  <br>
http://www.staff.dtu.dk/mpay  <br>
`r format(Sys.time(), "%a %b %d %Y, %H:%M:%S ")`

This notebook calculates some summary statistics about the total coverage of species examined in this work..


```{r}
#'========================================================================
# Setup ####
#'========================================================================
species.db <- readRDS(here("objects/Species_database.rds"))
value.sp.geo <- readRDS(here("objects/catch/value.species.country.rds"))
```

## Total Coverage 

How much of the total value of European fisheres is included in our analysis?

```{r}
total.value <- sum(value.sp.geo$value)
in.db <- filter(value.sp.geo,species %in% species.db$FAO_3A_code) 
sum(in.db$value)/total.value

```

## Coverage by country
```{r}
geo.coverage <- 
  value.sp.geo %>%
  mutate(in.db=species %in% species.db$FAO_3A_code) %>%
  group_by(geo,in.db) %>%
  summarise(total=sum(value)) %>%
  spread(.data$in.db,total) %>%
  mutate(prop=.data$"TRUE"/(.data$"TRUE"+.data$"FALSE")) 

ggplot(geo.coverage,aes(x=prop))+
#  stat_bin()+
  geom_rug()+
  stat_ecdf()

ggplot(geo.coverage,aes(geo,prop))+
  geom_bar(stat="identity")
```



***
*This work by Mark R Payne is licensed under a  Creative Commons
Attribution-NonCommercial-ShareAlike 3.0 Unported License. 
For details, see http://creativecommons.org/licenses/by-nc-sa/3.0/deed.en_US
Basically, this means that you are free to "share" and "remix" for 
non-commerical purposes as you see fit, so long as you "attribute" me for my
contribution. Derivatives can be distributed under the same or 
similar license.*

*This work comes with ABSOLUTELY NO WARRANTY or support.*

***



